---
title: "Peer Review Template"
author: "Marinos Ioannides"
date: "11/10/2021"
output: 
  word_document:
    toc: true
    number_sections: true
    reference_docx: template.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Create all the relevant external datasources here, checking to see if they already exist and not creating them if they do.
#The idea here is that when you sit down to use the template you have a series of documents with questions that need answering by you, the peer reviewer. 
#These documents and their answers will then inform the document and how it is filled in and should also inform your questioning.

create_check <- function(file_path, question_dataframe )
  if(!file.exists(file_path)){ #If the file does not exist, create it using the relevant questions
  readr::write_csv(question_dataframe, path = file_path)
  } else {
    stored_file <- readr::read_csv(file_path) #If the file does exist, compare the questions listed here with the questions it currently has asked
      if (isTRUE(dplyr::all_equal(stored_file[,1, drop = FALSE], question_dataframe[,1, drop = FALSE])) # Questions asked compared to the questions within this code.
    ) { 
    } else {
      readr::write_csv(question_dataframe, path = file_path)
    }
  }
  

template_manager <- 'Marinos Ioannides' #The individual who is responsible for maintaining this template
template_manager_email <- 'marinos.ioannides@ons.gov.uk' # The template manager's email for help with this template.
```

# Template Introduction {-}
This template is designed to aid peer reviewers in the writing and construction of their reports. It is *not* designed for model creators to cater their design to the demands of this document. 

For guidance on how to use R Markdown, please read this [very useful book](https://bookdown.org/yihui/rmarkdown/) which covers all the tools required and provides an excellent starting point for anybody using R Markdown. Guidance on how to code in R can be found [on the Learning Hub ](https://learninghub.ons.gov.uk/course/view.php?id=538) courtesy of the ONS team.

This template does not replace the need for competent and forensic peer review and can be added to by peer reviewers should they feel the need to. Indeed, if you notice inconsistencies, errors, absences or simply have questions about the template do not hesitate to email the template manager, `r template_manager`, at `r template_manager_email`.

Feel free to delete this section in the final submission to the modeling team.

# Peer Review Introduction

This peer review follows a Governance, Documentation & Functionality structure. This structure presents the systemic and structural issues first and foremost within the review, then the errors or absences within the documentation and concludes with the specific findings within the model. This structure emphasizes the systemic factors which are almost always involved in the most severe model errors and shortcomings and aim to highlight factors whose symptoms can be identified within models but whose root cause might otherwise go unnoticed.

This report assumes the reader has a basic understanding of the structure and function of the model. 

```{r Model Governance Overview, include=FALSE}
#Please supply the relevant answers here rather than in the text below.

SRO_name <- 'Dave Fakename' # Name of the SRO, leave as '' if none named.
AA_name <- ''  #Name of the analytical assurer, leave as '' if none named.
Commissioner_name <- '' #Name of the commissioner, leave as '' if none named.

#A function which fills in the names of the various named individuals
governance_presence_check <- function(role_name, role){
  return(ifelse(role_name == '',
                paste('there is no named', role),
                paste(role_name, ' is the model', role) 
                ))
}
#If there are absences in the governance structure, describes them and indicates the cause for concern.
absence_warning <- function(){
  return_string = ''
  if(SRO_name == ''){
    return_string <- paste('The absence of an SRO is very concerning for model governance and development. Without such a named individual, it is easy for errors to pass through the system undetected and presents a risk to model develpment. Furthermore, it is hard to see how work can be effectively signed off and reviewed without such a named individual.\n\n', return_string)
    }
  if(AA_name == ''){
    return_string <- paste('The absence of the analytical assurer is problematic. The analytical assurer exists to synthesise and review the assurance work of QA teams and previous peer review. Without such an individual it is easy for concerns raised by peer review to be forgotten or ignored. Their absence within this model and its governance structure is concerning to the peer review team.\n\n', return_string)
  }
  if(Commissioner_name == ''){
    return_string <- paste('The lack of a named commisisoner presents concerns to the peer review team. There should be a well documented and continous back and forth between the commissioner and the SRO to relay important discussions. Without such a named individual, it is difficult to see how the requirements of model users will be understood and satisfied by the modelling team. \n\n', return_string)
  }
  return(return_string)
}
#How have the individuals within the governance structure interacted?
#Please fill these in as TRUE or FALSE respectively
#This can be ignored if there is only one named indviidual from the above roster.
SRO_Commissioner_meeting <- FALSE



#Have the various groups been transmitting concerns to eachother correctly?
governance_interaction <- function(){
  
}

```

# Model Governance Overview

There are three key roles which should be filled by named, senior individuals according to modeling best practice, according to the Macpherson review. They are the Senior Responsible Owner (SRO), the Analytical Assurer (AA) and Commissioner.
In this model `r governance_presence_check(SRO_name, 'SRO')`, `r governance_presence_check(AA_name, 'AA')`, and `r governance_presence_check(Commissioner_name, "commissioner")`. 

`r absence_warning()`

The presence of named individuals comprises one part of model governance. How these individuals interact and govern the model is what ensures that the model is well managed or otherwise.

`r governance_interaction()`


``` {r Commissioner Governance, include = FALSE}
#This is a list of questions for commissioners  which should be asked by peer reviewers during their review. The answers to these questions can be placed here and will be automatically included where relevant. Non-answers will create automated concern messages.

#The peer reviewer must be able to grade the commissioning of this model on the following criteria

com_questions <- c('Team adequatelly resourced?',
                          "Was enough time allocated to the production of this model?",
                          "Was adequate time allocated for the quality assurance of this model?",
                          "Do the commissioner(s) well understand the limitations and caveats of the model?",
                          "Were assumptions discussed and well udnerstood in advance of model production?",
                          "Was the model development well planned from the start?",
                          "Were members of the team able to raise concerns with the commissioner?",
                          "Was there good communication between the Commissioner and the SRO?")

com_dataframe <- data.frame('Questions' = com_questions, 'Answers' = c('FALSE')) # We assume that all the answers are false unless proven otherwise.

create_check(file_path = "../model_information/com_questions.csv", question_dataframe = com_dataframe) #Checking to see if the file exists and, if it doesn't, it must be created.

commissioner_ans <- readr::read_csv("../model_information/com_questions.csv") #Reading back the answers and checking to see which ones are true and which ones are false to return the failures for the report
false_ans <-dplyr::filter(.data = commissioner_ans,
                              Answers == FALSE) #We want to list the shortcomings of the system rather than all the information.
```

## Commissioner Governance


`r if(nrow(false_ans)> 0){'This model does not meet the minimum best practice requirements of commissioner governance. \n The most clear failures were as follows \n'}else{'There were no obvious shortcomings noted as a result of commissioner governance.'}` 

`r if(nrow(false_ans)>0){knitr::kable(false_ans[,1:2])}`

`r if(Commissioner_name == ''){"The absence of a commissioner has significantly impaired model development."}`  

``` {r SRO Governance, include = FALSE}
#This is a list of questions for commissioners  which should be asked by peer reviewers during their review. The answers to these questions can be placed here and will be automatically included where relevant. Non-answers will create automated concern messages.

#The peer reviewer must be able to grade the commissioning of this model on the following criteria

SRO_questions <- c('Did the SRO relay team concerns well to the commissioner(s)?',
                   'Were the desires of the commissioner(s) well communicated to the modelling team?',
                   'Has the assumptions log been reviewed and signed off?',
                   'Is the assumption log up to date and of adequate detail and quality?',
                   'Have QA concerns been addressed and integrated into the model where relevant?')

SRO_dataframe <- data.frame('Questions' = SRO_questions, 'Answers' = c('FALSE'))

create_check(file_path = "../model_information/SRO_questions.csv", question_dataframe = SRO_dataframe)

SRO_ans <- readr::read_csv("../model_information/SRO_questions.csv")
false_ans <-dplyr::filter(.data = SRO_ans,
                              Answers == FALSE)
```
## SRO Governance 


`r if(nrow(false_ans)> 0){'This model does not meet the minimum best practice requirements of SRO governance. \n The most clear failures were as follows \n'}else{'There were no obvious shortcomings noted as a result of SRO governance.'}` 

`r if(nrow(false_ans)>0){knitr::kable(false_ans[,1:2])}`

`r if(SRO_name == ''){"The absence of an SRO has significantly impaired model development."}` 


``` {r AA Governance, include = FALSE}
#This is a list of questions for commissioners  which should be asked by peer reviewers during their review. The answers to these questions can be placed here and will be automatically included where relevant. Non-answers will create automated concern messages.

#The peer reviewer must be able to grade the commissioning of this model on the following criteria

AA_questions <- c('Was all formal QA work reviewed by the AA?',
                  'Were the recommendations of QA work implemented or the lack of implentation justified?',
                  'Have the changes implemented as a result of QA been signed off by the AA?',
                  'Was adequate time allocated to perform QA?',
                  'Was time allocated for the consideration and implementation of QA findings?',
                  'Has adequate time been allocated to implement the findings of this review?')

AA_dataframe <- data.frame('Questions' = AA_questions, 'Answers' = c('FALSE'))

create_check(file_path = "../model_information/AA_questions.csv", question_dataframe = AA_dataframe)

AA_ans <- readr::read_csv("../model_information/AA_questions.csv")
false_ans <-dplyr::filter(.data = AA_ans,
                              Answers == FALSE)
```
## Analytical Assurer Governance

`r if(nrow(false_ans)> 0){'This model does not meet the minimum best practice requirements of AA governance. \n The most clear failures were as follows \n'}else{'There were no obvious shortcomings noted as a result of AA governance.'}` 

`r if(nrow(false_ans)>0){knitr::kable(false_ans[,1:2])}`

`r if(SRO_name == ''){"The absence of an AA has significantly impaired model development."}` 

## Governance Summary 



# Documentation Overview

Documentation acts not only acts as a useful audit trail for peer reviewers but helps remind modeling teams of the current best practices.If information is not document properly it cannot be proven to ourselves or the taxpayer that the information was gathered, considered and included in the decision making process. Any gaps in documentation are considered to be gaps in the model structure.

``` {r Assumptions log, include = FALSE}
 #The criteria we deem important for the assumptinos log.
assumption_criteria <- c( 'Name',
                                       'Rationale' ,
                                       'Location',
                                       'Value(and range)',
                                       'Error_probability',
                                       'Sensitivity' ,
                                       'Risk_score' ,
                                       'Sign_off(SRO)',
                                       'Peer_Review_addition') # The criteria we want to know for each assumption

#TODO: Add a way of checking to see if the assumptions log exists.
fresh_log = data.frame(matrix(nrow = 10, ncol = length(assumption_criteria)))
colnames(fresh_log) = assumption_criteria
assumptions_log_path <- "../model_information/assumptions_log.xlsx"

writexl::write_xlsx(fresh_log, assumptions_log_path)

assumptions_log <- readxl::read_excel(assumptions_log_path)
assumptions_log
missed_assumptions <- dplyr::filter(.data = assumptions_log,
                                    Peer_Review_addition  == TRUE)
missed_assumptions$Name
```
## Assumptions Log

The assumptions log acts as a store of the model's assumptions. In general there can be two kinds of errors in the assumptions log - absent assumptions or incorrectly recorded assumptions.

### Absent Assumptions

Absent assumptions are those assumptions which are detected by the peer reviewer but are not present within the assumptinos log. This implies that there are assumptions which have not been considered by the modelling team and may be causing significant bias within the model structure and function.

The following assumptions were detected by the peer reviewer yet were not listed in the assumptions log.






### Incorreclty Recorded Assumptions

## Input Quality Review
## Commissioning Document
## Sensitivity Analysis
## User Report

## Documentation Summary

# Functionality Overview 

## Rationale
## Code
## Input quality
## Relation to documentation

# Summary

## Governance
## Documentation
## Functionality

# Recommendations



